---
title: "RTextCleaner: Text Processing and Cleaning Package"
author: "Jane Shen, Jingran Zhao, Skylar Shao"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{RTextCleaner: Text Processing and Cleaning Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE}
devtools::load_all()
library(RTextCleaner)
Sys.setenv(GEMINI_API_KEY = "AIzaSyBnvClxUt8sB5VfOechJ9o-YgFVhLss_Ow")
```

## Introduction

`RTextCleaner` is an R package designed for efficient text processing and cleaning. It includes functions to:
- Separate code from text
- Remove noise
- Normalize text
- Perform sentiment analysis
- Simplify text
- Visualize token frequency changes before and after processing

These features help users prepare raw text for analysis, making it particularly useful for **Natural Language Processing (NLP)** tasks and cleaning text data.

## Installation

To install `RTextCleaner`, run:

```r
remotes::install_github("yourusername/RTextCleaner")
```

## Usage Examples

### 1. Separating Code from Text

The `separate_code_prompt` function extracts programming code from natural language text.

```{r}
text_sample <- "Here is some text. ```python print('Hello, World!') ```"
result <- separate_code_prompt(text_sample)
print(result)
```

#### Test Case
```{r}
test_that("separate_code_prompt works correctly", {
  test_input <- "Here is a simple Python function:\n```python\ndef add(a, b):\n    return a + b\n```"
  
  mock_response <- list(
    candidates = list(
      list(content = list(
        parts = list(
          list(text = '{"text": "Here is a simple Python function:", "code": "def add(a, b):\n    return a + b"}')
        )
      ))
    )
  )
  
  stub(separate_code_prompt, "httr::POST", function(...) {
    structure(list(status_code = 200), class = "response")
  })
  stub(separate_code_prompt, "httr::content", function(...) mock_response)
  
  result <- separate_code_prompt(test_input)
  expect_equal(result$text, "Here is a simple Python function:")
  expect_equal(result$code, "def add(a, b):\n    return a + b")
})
```

### 2. Removing Noise from Text

```{r}
noisy_text <- "OMG!!!!! This is soooo cooool!!!"
cleaned_text <- gemini_remove_noise(noisy_text)
print(cleaned_text)
```

#### Test Case
```{r}
test_that("gemini_remove_noise works correctly", {
  test_input <- "OMG!!!!! This is soooo cooool!!!"
  expected_output <- "OMG! This is so cool!"
  
  mock_response <- list(
    candidates = list(
      list(content = list(
        parts = list(
          list(text = expected_output)
        )
      ))
    )
  )
  
  stub(gemini_remove_noise, "httr::POST", function(...) {
    structure(list(status_code = 200), class = "response")
  })
  stub(gemini_remove_noise, "httr::content", function(...) mock_response)
  
  result <- gemini_remove_noise(test_input)
  expect_equal(result, expected_output)
})
```

### 3. Normalizing Text

```{r}
text_samples <- c("omg dis is da best day evr!!!", "yayyy, tysm this is sooo gr8!!!")
normalized_text <- gemini_text_normalization(text_samples)
print(normalized_text)
```

### 4. Sentiment Analysis

```{r}
text_samples <- c("I love pizza, sushi, and burgers!", "I hate horror movies. They're terrible.")
sentiment_results <- gemini_sentiment_analysis(text_samples)
print(sentiment_results)
```

### 5. Text Simplification

```{r}
complex_text <- "Quantum computing leverages the principles of quantum mechanics to perform computations exponentially faster than classical computers."
simplified_text <- gemini_text_simplification(complex_text)
print(simplified_text)
```

### 6. Visualizing Token Frequency Before and After Processing

```{r}
visualize_normalization(top_n = 20)
```

## Conclusion

The `RTextCleaner` package provides powerful text processing tools that enhance NLP workflows. It includes functions for **text normalization, noise removal, sentiment analysis, and visualization** to improve data quality for analysis.

For issues or contributions, visit the [GitHub Repository](https://github.com/j232shen/RTextCleaner).
